\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-28 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_10pg.tex
updates

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
To highlight the scalability of the proposed method, we next consider a power network with $n=50$ generators, and propagate the transient joint state PDFs supported over the 100 dimensional state space $\mathbb{T}^{50}\times\mathbb{R}^{50}$. We take the initial joint state PDF at $t=0$ as
% \begin{align}
% \rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
% 	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
% \label{rho0synthetic}	
% \end{align}
\begin{multline}
\rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right) \\
	\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{multline}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

\bibitem{halder2021stochasticExpanded}
A.~Halder, K.F.~Caluya, P.~Ojaghi, and X.~Geng, ``Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions", \emph{extended preprint}, \\
URL: \url{http://dx.doi.org/10.13140/RG.2.2.30956.28805}, 2021.

>>>>

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
To highlight the scalability of the proposed method, we next consider a power network with $n=50$ generators, and propagate the transient joint state PDFs supported over the 100 dimensional state space $\mathbb{T}^{50}\times\mathbb{R}^{50}$. We take the initial joint state PDF at $t=0$ as
% \begin{align}
% \rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
% 	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
% \label{rho0synthetic}	
% \end{align}
\begin{multline}
\rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right) \\
	\qquad\times {\rm{Unif}}\left(\left([-0.1,0.1]\;\text{rad/s}\right)^{n}\right),
\label{rho0synthetic}	
\end{multline}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

\bibitem{halder2021stochasticExpanded}
A.~Halder, K.F.~Caluya, P.~Ojaghi, and X.~Geng, ``Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions", \emph{extended preprint}, \\
URL: \url{http://dx.doi.org/10.13140/RG.2.2.30956.28805/1}, 2021.
